### 2018-08-08 paper/evaluation.tex
eval in progress

All our experiments were conducted with 25 users participating in \name. 
The files exchanged are a collection of 12 real ones, ranging from 5KB to 640MB.

@@

@@

Overall, we saw 94\% of successful file transfer.

\begin{figure}[t]
  \centering
  %\def\svgwidth{0.8\columnwidth}
  \includegraphics[width=0.8\columnwidth]{figures/logistic_many_0-001.pdf}

  \caption{\label{fig:logistic}
  Logistic regression of the success rate as a function of the file size using the default parameters.}
\end{figure}

Figure~\ref{fig:logistic} shows the logistic regression of the success rate as a function of the files' size. 
This regression is good candidate to describe binary stochastic processes as a function of a dependent variable,
and is often used in epidemics prediction, economics, and even marketing.
Simply put, given $X$ (in our case, the size of each transfered file) and $y$ (the outcome of the transfer: success or failure), 
the regressor estimates the coefficient $k$ and the mid-point $x_0$ of the logistic function defined as follows:

$$ f(x) = \frac{1}{1 + e^{-k \cdot x + x_0 }} $$

Because it sets the top (100\%) and bottom (0\%) values as asymptotes, 
logistic regression does not yield very optimistic success rates at the beginning,
but its midpoint $x_0$ tends to be very accurate even with a low quantity of training samples.
\commentAL{Yes indeed, very pessimistic, where is our 94\%!? I want to make a CDF also.}

In our case, $f(x)$ reads the probability that a file exchange fails given its size. 
The plot reads that files below 319MB have more than 90\% chances of being successfully exchanged.
The probability falls as the file gets bigger, such that a 1,O43MB has 50\% chances of successful transfer (see $x_0$).

  \caption{\label{fig:bw_and_pending_files}Traffic during one experiment.
  In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
\end{figure}

>>>>

All our experiments were conducted with 25 users participating in \name. 
The files exchanged are a collection of 12 real ones, ranging from 6KB to 640MB.

@@

\subsubsection{Experimental process} % (fold)
\label{ssub:experimental_process}

  \caption{\label{fig:bw_and_pending_files}Timeline of one experiment's traffic.
  In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
\end{figure}

The experiments were conducted as follows: 
\begin{itemize}
  \item A first initialization procedure takes care of bootstrapping the users and their devices. 
  A scheduler is started for each user, that will turn devices on or off throughout the experiment according to the models discussed in~\ref{ssub:simulating_user_behavior};
  \item The 12 file exchanges are initiated in turn: a couple $(d_s, d_r)$ of online devices from different users is chosen.
  The sender $d_s$ is requested to initialize file upload
\end{itemize}

% subsubsection experimental_process (end)

@@

Figure~\ref{fig:completion_vs_size} first shows the success rate of each exchanged file over the 30 experiments.
The dotted black line shows the overall success rate: 94.4\%. 
Each bar shows the individual success rate of our test files, with their size on the x-axis.
As one can see, the success rate drops as files get bigger.
Files bigger than 112MB show a success rate between 80 and 90\%, while all lighter files are successfully transfered in 90\% of the cases at least.

% \begin{figure}[t]
%   \centering
%   %\def\svgwidth{0.8\columnwidth}
%   \includegraphics[width=0.8\columnwidth]{figures/logistic_many_0-001.pdf}

%   \caption{\label{fig:logistic}
%   Logistic regression of the success rate as a function of the file size using the default parameters.}
% \end{figure}

% Figure~\ref{fig:logistic} shows the logistic regression of the success rate as a function of the files' size. 
% This regression is good candidate to describe binary stochastic processes as a function of a dependent variable,
% and is often used in epidemics prediction, economics, and even marketing.
% Simply put, given $X$ (in our case, the size of each transfered file) and $y$ (the outcome of the transfer: success or failure), 
% the regressor estimates the coefficient $k$ and the mid-point $x_0$ of the logistic function defined as follows:

% $$ f(x) = \frac{1}{1 + e^{-k \cdot x + x_0 }} $$

% Because it sets the top (100\%) and bottom (0\%) values as asymptotes, 
% logistic regression does not yield very optimistic success rates at the beginning,
% but its midpoint $x_0$ tends to be very accurate even with a low quantity of training samples.
% \commentAL{Yes indeed, very pessimistic, where is our 94\%!? I want to make a CDF also.}

% In our case, $f(x)$ reads the probability that a file exchange fails given its size. 
% The plot reads that files below 319MB have more than 90\% chances of being successfully exchanged.
% The probability falls as the file gets bigger, such that a 1,O43MB has 50\% chances of successful transfer (see $x_0$).

% ------------------
